An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-01-16 paper/answer_reviewers.tex

\textbf{Reviewer 1}

\bigskip

\textit{Figure 1: Depth contour of subducting plate and surface traces of the San Andreas fault zones (SAF) should be in the figure for easier understanding because authors mentioned about LFE families are on SAF and in the subduction zones (Lines 176 - 183). It should be also helpful to include a figure of depth cross section for LFE hypocenters.}

We added the depth contours of the plate boundary model from McCrory et al. (2006) and fault lines. We added a cross section with the depth of the LFE families.

@@

\bigskip

\textit{Figure 2: It is helpful to show the value of the detection threshold in this figure.}

\bigskip

We analyzed the seismic data one hour a time. For each hour of data, we assumed that there was an LFE each time the average cross-correlation over all stations and channels is higher than 8 times the median absolute deviation. The threshold is thus different for each hour of data and it is difficult to show its values in the figure.

@@

\bigskip

\textit{Lines 165 - 175: How second thresholds (CC values vs stations numbers) were chosen for each seismic station? If it is done manually, please provide a list of the threshold as the supplementary table. In addition, how many events did this selection step remove from the catalog? (A figure comparing before and after the selection step will be useful.)}

The choice of the threshold is explained in more detail later in the text, when we explain how we cleaned the longer catalog (2004-2011). The main idea is that if an LFE is present both in the 2007-2009 FAME catalog and in the 2004-2011 permanent networks catalog, then it is unlikely to be a false detection. We assumed that all LFEs present in both catalogs are true detections. The LFEs recorded during the period 2007-2009 that are present in only one catalog are then assumed to be false detections. We then chose a threshold such that at least 50 \% of the LFE detections are true detections. There is thus one threshold per family. The thresholds are also different for the two catalogs 2007-2009 and 2004-2011 because the stations and the quality of the templates are different for both catalogs. We added in a supplement a table with the values of the thresholds. \\

Our filtering method kept 37 \% of the LFEs for the 2004-2011 catalog and 16 \% of the LFEs for the 2007-2009 catalog. We have added in the supplements figures of the catalogs without filtering the LFEs.

@@

\bigskip

\textit{Lines 204 - 207: How much are two catalogs (the FAME catalog and the network catalog) different originally? As the station density of FAME stations seems to be equivalent to that of permanent stations, I expect two catalogs do not show significant differences. If there are severe differences between two catalogs, detection process and/or event selection procedure needs to be reconsidered. In addition, I think it is also good to show event catalog detected using both FAME stations and permanent stations. Comparing "FAME + network" catalog and the network catalog at the same period, we can evaluate how much the resolution of LFE detection only with the permanent stations becomes worse than that with additional FAME stations. This is important information to evaluate completeness of the LFE catalog in the periods without FAME stations.}

\bigskip

We have computed the catalog with only the FAME stations and the catalog with only the permanent stations. We have not computed a catalog using both FAME and permanent stations. We agree that it would be interesting to compute this third catalog and study how many LFEs are missed when removing the FAME stations, but this is beyond the scope of this paper.

@@

\bigskip

\textit{Line 209: "two thresholds" for what?}

\bigskip

One threshold to filter the 2007-2009 catalog computed with the FAME stations and one threshold to filter the 2004-2011 catalog computed with the permanent stations. We use two different thresholds because the quality of the templates is not the same for the two catalogs.

@@

\bigskip

\textit{Line 215: It will be helpful to visually show temporal changes of the number of available seismic stations.}

We have added two figures in the supplement with number of channels available as a function of time.

@@

\bigskip

\textit{Lines 271 - 273: Is there no evidence for dynamic triggering as well?}

\bigskip

We did not see any burst of LFEs coincident with the arrival of seismic waves from regional or distant earthquakes.

@@

\bigskip

\textit{Lines 290 - 294: I think the vertical axis of Figure 9 should be average recurrence interval rather than the number of events.}

We changed the figure and plotted recurrence time instead of number of events.

@@

We added these references.

\bigskip

\textit{Line 306: Which fault plane did authors assume to calculate tidal stress?}

The fault plane is the plate boundary model of McCrory et al. (2006).

@@

\bigskip

\textit{Line 290 / Figure 9: I'm a bit confused here. The number of LFE events shown on Figure 9 (< 50) are much too small to be total numbers of events, as made clear by the daily event counts in Figure 8... Are these LFE numbers normalized somehow? Please clarify this.}

\bigskip

To define the number of events, we assume that there is an event each time that there are at least five LFEs during a single day. If two events are separated by less than five days, we assume that this is a single event. We remade the figure to plot average recurrence time instead of number of events.

@@

\bigskip

\textit{Line 173: "The threshold is thus different for each LFE family". I'm not sure what you mean here. Is the threshold constant for each family, or does it vary as stations become active/inactive? Is the threshold consistent for a given number of active stations (on that day), or does it vary between templates? Please try to clarify.}

\bigskip

To keep an LFE in the filtered catalog, we require that the product of the cross-correlation by the number of channels recording at that time is higher than a threshold. We thus require a higher cross-correlation value to keep the LFE in the catalog if some stations are inactive. The threshold is different for each LFE family and applied to the stacked cross-correlation over all channels.

@@

\bigskip

\textit{Line 180: "Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families." What locations are you using here? Also, maybe for clarity you can put (40.1N), or whatever the precise latitude is after "...on the southern end". It may be good to specify the depth here too, since it may not be surprising to see frequent bursts if the family is at 45 km depth.}

We use the same locations as Pourde et al. (2015). We have not tried to relocate the families using the new templates. We specified the latitude and depth of the family in the text.

@@

\bigskip

\textit{Line 312: "We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity." It's not clear to me why this (the black lines in Figure 10) varies so dramatically between families, could you explain a bit further?}

\bigskip

We divided possible values of the Coulomb stress changes into bins and computed the number of hours for which the Coulomb stress change takes values in each bins. As Coulomb stress change often takes small values and rarely takes high values, the expected number of LFEs is higher around 0 and smaller for big negative or positive values. We did not normalize the results, so the expected number of LFEs is proportional to the total number of LFEs occurring for each family.

### 2022-01-16 paper/agujournaltemplate_highlighted.tex
Finished draft of revisions

\authors{Ariane Ducellier\affil{1}, Kenneth Creager\affil{1}}

@@

Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes. Their occurrence is often associated with tectonic tremor and slow slip events along the plate boundary in subduction zones and occasionally transform fault zones. They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface and recurring more or less episodically in a bursty manner. In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011. As in northern Cascadia, the down-dip LFE families have \textbf{shorter recurrence intervals} than the up-dip families. For the April 2008 Episodic Tremor and Slip event, the best recorded LFE families exhibit a strong tidal stress sensitivity. The southernmost LFE family, which has been interpreted to be on the subduction plate boundary has a short recurrence time. Also, these LFEs tend to occur during times when tidal stress discourages slip on the plate boundary. Both observations suggest this LFE family may be on a different fault.

@@

~\citeA{PLO_2015}) have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME). They used a combination of autodetection methods and visual identification to obtain the initial templates. Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation. They found that the LFE families on the southern Cascadia Subduction Zone were located above the \textbf{plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km). However, they suggested that this may be because the model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1.5cm 4cm 1cm 10cm},clip]{figures/map_LFEs.eps}
\caption{Map showing the location of the LFE families (back dots) and the seismic stations used in this study. Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations. Red stars are moderate ($M > 5$) nearby earthquakes.}
\label{pngfiguresample}
\end{figure}

@@

We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating. Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog. As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the cross-correlation value by the number of stations recording at that time is higher than a threshold. The threshold is thus different for each LFE family. The resulting LFE catalog for the period 2007-2009 is shown in Figure 3. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. \\

@@

We note that there is a good spatial and temporal agreement between tremor and LFEs, with LFEs detected during the main tremor episodes. Additional small LFE episodes are also detected between bigger tremor episodes. The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone. Additionally, one LFE family located on the southern end of the subduction zone has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families. \\

@@

For most families, we find that we can obtain good templates with signal-to-noise ratio for several stations. Only nine families have four or less seismic stations with good templates. Examples of templates are given in Figure 4 for station WDC and family A (square in Figure 1). To obtain the above catalog, we used one-minute-long templates, which included noise before and after the seismic wave arrivals. To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations. We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio. We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009. \\

@@

For most of the families located on the subduction zone, we obtained a good agreement between both catalogs. We eliminate two families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates. However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network. We are thus confident that we can detect LFEs before 2007 and after 2009. In the following, we focus on the period 2004-2011. In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE event after that date. The resulting LFE catalog for the period 2004-2011 is shown in Figure 6. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/zoom_ETS_events.eps}
\caption{LFE and tremor detections as a function of time and latitude for six ETS events. Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}. Black dots represent days where LFEs are detected for a given LFE family. The size of the black dots are proportional to the number of LFEs detected during this day. For clarity, we do not show the LFEs for the days when there are less than three LFEs. \textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005. This is why no tremor detections can be shown or the two events in 2004.}}
\label{pngfiguresample}
\end{figure}

@@

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different from each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the number of LFE events as a function of the distance in the eastern direction from the upper limit of the tremor. We clearly see that the number of events increases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
\caption{Number of LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1). Family A (square in Figure 1) has much more LFE events and is shown by an arrow.}
\label{pngfiguresample}
\end{figure}

@@

where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}. We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient \textbf{, as was done by ~\citeA{HOU_2015}}. We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin. We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity. As noted by ~\citeA{HOU_2015}, tremor sensitivity to stress perturbations changes during an ETS event, with an increase in sensitivity to tidal stress as slip accumulates over several days. We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front. As there are only a few LFEs, it is not always obvious to see the influence of tidal stress on LFE activity. However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs. For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity. However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity. To better highlight the behavior of family A, we also consider the whole LFE catalog and plot the observed and expected number of LFEs as a function of tidal stress. We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary. We hypothesize that LFE family A may not be located on the subduction zone, and may be on a different fault instead.

@@

\acknowledgments
The authors would like to thank A. Plourde for sharing his low-frequency earthquake catalog, D. Boyarko for sharing his tremor catalog, and H. Houston for the tidal stress calculation in the Cascadia subduction zone. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings from the FAME experiment used for this analysis can be downloaded from the IRIS website \cite{https://doi.org/10.7914/sn/xq_2007}. Waveform data from the permanent networks were accessed through the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC. The first figure was done using GMT ~\cite{WES_1991}. \textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.

>>>>

\authors{Ariane Ducellier\affil{1}, Kenneth C. Creager\affil{1}}

@@

Low-frequency earthquakes (LFEs) are small magnitude earthquakes, with typical magnitude less than 2, and reduced amplitudes at frequencies greater than 10 Hz relative to ordinary small earthquakes. They are usually grouped into families of events, with all the earthquakes of a given family originating from the same small patch on the plate interface. \textbf{LFEs tend to happen in bursts, with dozen of earthquakes occurring within a few days, followed by weeks or months of quiet}. In this study, we extend the LFE catalog obtained by ~\citeA{PLO_2015} to the 8-year period 2004-2011. As in northern Cascadia, the \textbf{LFE families located at greater depth are more active, with shorter time intervals between two earthquake bursts, than the LFE families located at shallower depth. Earth tides have also an influence on LFE activity: LFEs are more likely to occur when the stress changes associated with the tides favor shear failure on the plate boundary}.

@@

~\citeA{PLO_2015} have detected LFEs in southern Cascadia during the April 2008 ETS event using seismic data from the EarthScope Flexible Array Mendocino Experiment (FAME). They used a combination of autodetection methods and visual identification to obtain the initial templates. Then, they recovered higher signal-to-noise LFE signals using iterative network cross-correlation. They found that the LFE families on the southern Cascadia Subduction Zone were located above the \textbf{plate boundary model of ~\citeA{MCC_2006}, with a large distribution of depths (28-47 km). However, they suggested that this may be because the model is biased deep.} Three additional LFE families were found on two strike-slip faults, the Maacama and Bucknell Creek faults, which are part of the San Andreas Fault zone. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0.5cm 7cm 1.5cm 7cm},clip]{figures/map_LFEs.eps}
\caption{Map showing the location of the LFE families (black dots) and the seismic stations used in this study. Red triangles are the stations from the FAME experiment, green triangles are one-component permanent stations, blue triangles are three components permanent stations. Red stars are moderate ($M > 5$) nearby earthquakes. \textbf{Contour lines are the depth contours of the plate boundary model from ~\citeA{MCC_2006}. The cross section shows the depth of the LFE families. The line corresponds to the plate boundary model from ~\citeA{MCC_2006} at latitude 41N.}}
\label{pngfiguresample}
\end{figure}

@@

We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating. Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog. As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the \textbf{stacked} cross-correlation value by the number of \textbf{channels} recording at that time is higher than a threshold. \textbf{We will explain later in the text how the threshold is chosen}. The threshold is different for each LFE family, \textbf{but is constant over time for a given LFE family}. The resulting LFE catalog for the period 2007-2009 is shown in Figure 3. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. \textbf{Filtering the catalog has removed about 84 \% of the LFEs. As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\

@@

We note that there is a good spatial and temporal agreement between tremor and LFEs, with LFEs detected during the main tremor episodes. Additional small LFE episodes are also detected between bigger tremor episodes. The LFE families located south on the strike-slip fault from the San Andreas Fault system have much shorter recurrence intervals than the LFE families located on the subduction zone. Additionally, one LFE family located on the southern end of the subduction zone \textbf{(family A at 40.09N and 34.9km depth)} has also shorter recurrence intervals than families located farther north, and behaves more similarly to the strike-slip fault families. \\

@@

For most families, we find that we can obtain good templates with high signal-to-noise ratio for several stations. Only nine families have four or less seismic stations with good templates. Examples of templates are given in Figure 4 for station WDC and family A (square in Figure 1). To obtain the above catalog, we used one-minute-long templates, which included noise before and after the seismic wave arrivals. To increase the cross-correlation values between the templates and the data, we thus reduced the length of the templates to 25 to 40 seconds, depending on the maximum distance from the source to the stations. We did not use stations more than 100 kilometers away from the epicenter of an LFE family, as the template would be unlikely to have a good signal-to-noise ratio. We then used this new, shorter templates for the permanent stations to make an LFE catalog for the period 2007-2009. \\

@@

For most of the families located on the subduction zone, we obtained a good agreement between both catalogs. We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates. However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network. We are thus confident that we can detect LFEs before 2007 and after 2009. In the following, we focus on the period 2004-2011. In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE events after that date. The resulting LFE catalog for the period 2004-2011 is shown in Figure 6. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008. \textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above. Filtering the catalog has removed about 63 \% of the LFEs. As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/zoom_ETS_events.eps}
\caption{LFE and tremor detections as a function of time and latitude for six ETS events. Red dots represent tremor detections from the catalog of ~\citeA{BOY_2015}. Black dots represent days where LFEs are detected for a given LFE family. The size of the black dots are proportional to the number of LFEs detected during this day. For clarity, we do not show the LFEs for the days when there are less than three LFEs. \textbf{The tremor catalog of ~\citeA{BOY_2015} starts in 2005. This is why no tremor detections can be shown for the two events in 2004.}}
\label{pngfiguresample}
\end{figure}

@@

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor. We clearly see that the \textbf{average time between} decreases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/nb_LFE_events.eps}
\caption{\textbf{Average time between} LFE events as a function of distance in the eastern direction from the \textbf{westward} limit of tremor for the three LFE families in group B (triangles in Figure 1), the five LFE families in group C (diamonds in Figure 1), and the five LFE families in group G (pentagons in Figure 1). Family A (square in Figure 1) has much \textbf{shorter time intervals between } LFE events.}
\label{pngfiguresample}
\end{figure}

@@

where $\Delta \tau$ is the change in shear stress on the fault plane in the slip direction, $\Delta \sigma$ is the change in fault normal stress (positive is tensile), $\mu$ is the coefficient of intrinsic friction, $\Delta \sigma_m$ is the change in mean stress and $B$ is the Skempton's coefficient ~\cite{HOU_2015}. We take the values $\mu = 0.1$ and $B = 0.5$ for the friction and the Skempton's coefficient, \textbf{as was done by ~\citeA{HOU_2015}}. We then divided the values of tidal Coulomb stress change into 20 stress bins and computed for each LFE family the number of LFEs occurring at a time when the value of the stress was in a given bin. We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity. As noted by ~\citeA{HOU_2015}, tremor sensitivity to stress perturbations changes during an ETS event, with an increase in sensitivity to tidal stress as slip accumulates over several days. We thus choose to only consider the later part of the 2008 ETS event, using only LFEs that occurred between 1.5 and 11.5 days after the arrival of the tremor front. As there are only a few LFEs, it is not always obvious to see the influence of tidal stress on LFE activity. However, Figure 10 shows the number of LFEs occurring during each stress bin (blue bars) and the expected number of LFEs (black line) for six families with a relatively high number of LFEs. For most of the families, a positive Coulomb stress change (promoting shear failure) is associated with an increase in LFE activity. However, this is not the case for the southernmost LFE family A, for which a negative Coulomb stress change is associated with an increase in LFE activity. To better highlight the behavior of family A, we also consider the whole LFE catalog and plot the observed and expected number of LFEs as a function of tidal stress. We clearly see that these LFEs tend to occur during times when predicted tidal Coulomb stress is discouraging slip on the plate boundary. We hypothesize that LFE family A may not be located on the subduction zone, and may be on a different fault instead.

@@

\acknowledgments
The authors would like to thank A. Plourde for sharing his low-frequency earthquake catalog, D. Boyarko for sharing his tremor catalog, and H. Houston for the tidal stress calculation in the Cascadia subduction zone. The authors would like to thank Alexandre Plourde, an anonymous reviewer and the associate editor whose comments helped improve the manuscript. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings from the FAME experiment used for this analysis can be downloaded from the IRIS website \cite{https://doi.org/10.7914/sn/xq_2007}. Waveform data from the permanent networks were accessed through the Northern California Earthquake Data Center (NCEDC), doi:10.7932/NCEDC. The first figure was done using GMT ~\cite{WES_1991}. \textbf{All the downloading and preprocessing operations on the seismic waveforms are done with the Python package obspy.} The Python scripts used to analyze the data and make the figures can be found on the first author's Github account, accessible through Zenodo ~\cite{ariane_ducellier_2021_5168867}.
